---
title: "Poke API Vignette"
author: "Evan Patton"
date: "9/27/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE)
```


## Introduction

This space reserved for introduction, talk about the project, my thoughts, and then an overview of my work.



## Packages Needed

In this Vignette we will need the following packages:

```{r packages}
# You only need to run the install.packages() functions if you have not already downloaded the packages. 
# As I already have them downloaded, I am not doing that here. 
# If you need to, copy and paste the line needed, without the #, into your console and run.

# install.packages("tidyverse")
# install.packages("httr")
# install.packages("jsonlite")
# install.packages("knitr")

library(httr)
library(jsonlite)
library(tidyverse)
library(knitr)
```

# Building the Functions

## Encounter Function

Pokemon fans around the world, myself included, know the catch phrase from the TV show by heart. **"Gotta Catch 'em All"**.
That speaks to a major part of both the Pokemon TV shows and the video games, which is collecting all the different Pokemon from around the fictional world and filling up your PokeDex with their information.

However, before you can catch 'em, you gotta find 'em. That is the purpose of this function is to find what locations in games you can find Pokemon in the wild. It will also return the chance of encountering the Pokemon there, the minimum level, the maximum level, and how you would encounter the Pokemon (walking in tall grass vs being given as a gift as an example.)


The function `encounter` is built below and an example will be shown later. `encounter` takes two arguments, the first one is not optional, and that is the Pokemon you want to find. The second argument is optional, and that is what game from the series you want to return data on, if no game is selected then all games will be returned in the final tibble. **Both arguments require quoted strings**

```{r encounter_func}

# Starting the function
encounter <- function(poke, game = "all") {

# Converting inputs to lower case for flexability
poke <- tolower(poke)
game <- tolower(game)

# Get the requested data   
raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/pokemon/",poke,"/encounters"), flatten = TRUE)


# Start loops.
# Beginning of location loop.
for (i in 1:dim(raw_data)[1]) {
  
  # Get the location from raw.
  loc <- raw_data[i,2]
  
  # Beginning of game loop.
  for (b in 1:dim(raw_data[[1]][[i]])[1]){
    
    # Get the specific game from raw.
    gm <- raw_data[[1]][[i]][b,3]
    
    # Beginning of details loop.
    for (a in 1:dim(raw_data[[1]][[i]][[1]][[b]])[1]){
      
      # Get the chance, max level, min level, and method.
      chance <- raw_data[[1]][[i]][[1]][[b]][a,1]
      max    <- raw_data[[1]][[i]][[1]][[b]][a,3]
      min    <- raw_data[[1]][[i]][[1]][[b]][a,4]
      meth   <- raw_data[[1]][[i]][[1]][[b]][a,5]
      
      # Combine all vars into a line for tibble creation
      line   <- c(loc,gm,chance,max,min,meth)
         
      # Build dfd tibble.
      # If this is the first iteration of the details loop
      # then dfd is created with all of the vars.
      # If not first iteration, bind dfd with line to add another line to dfd.
      if(a == 1){
        dfd <- tibble(loc,gm,chance,max,min,meth)
      } else{
          dfd <- rbind(dfd,line)
        } # Close if else statement.
      } # Close details loop.
  
    # Build dfg tibble.
    # If first iteration of game loop, dfg is dfd.
    # If not first iteration, dfg is binded with dfd to add more lines.
    if(b == 1)
    {dfg <- dfd
    }else{
      dfg <- rbind(dfg,dfd)
    } # Close if else statement
    } # Close game loop
    
  # Create final tibble
  # If first iteration of location loop, dfl is the final dfg from the game loop.
  # If not first iteration, dfl is binded with the most recent dfg to add more lines.
  if(i==1){
    dfl <- dfg
  }else{
    dfl <- rbind(dfl,dfg)
  } # End if else statement
  } # End location loop
# End of all loops

# Rename variables in final dfl.
names(dfl) <- c("Location","Game","Chance","Max_Level","Min_Level","Method")

# Keep only distinct rows, as there are some that repeat due to variables 
# not important for this function.
dfl <- distinct(dfl)

# If user doesn't input an option for game or wants all games, dfl is returned.
# If user does input an option for game, then dfl is filtered for that game and returned.
if(game == "all"){
   return(dfl)
}else{
    return(dfl %>%
             filter(Game == game))
  } # End of if else statement.

} # Close of function.
```




## Stats Function

Another major portion of the Pokemon video games is battling. During a battle you want to make sure you have the strongest Pokemon, the way their strength is determined is through their "base stats". 

Their base stats are:  
* [HP](https://bulbapedia.bulbagarden.net/wiki/Stat#HP)  
* [Attack](https://bulbapedia.bulbagarden.net/wiki/Stat#Attack)  
* [Defense](https://bulbapedia.bulbagarden.net/wiki/Stat#Defense)  
* [Special Attack](https://bulbapedia.bulbagarden.net/wiki/Stat#Special_Attack)  
* [Special Defense](https://bulbapedia.bulbagarden.net/wiki/Stat#Special_Defense)  
* [Speed](https://bulbapedia.bulbagarden.net/wiki/Stat#Speed)

You can read about what each one means by clicking on their names as they are links to the Bulbapedia website which is a treasure trove of Pokemon knowledge.

The `stats` function  is built below and it will return this information about the Pokemon the user chooses. The function takes a single argument which is `poke` this can be a either a single character string or a vector of them if you want to return the details about more Pokemon.



```{r stats_function}

# Create the function
stats <- function(poke) {
  
  # Looping for entrance of a vector
  for(i in 1:length(poke)){
  
    # Get requested data from API
  raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/pokemon/",poke[i]), flatten = TRUE)

  # Select only the information about the base stats
  df <- as_tibble(raw_data[["stats"]])
  
  # Add a column for the name of the Pokemon 
  df$name <- str_to_sentence(poke[i])
  
  # Keep only needed columns and reorder
  df <- df[,c(5,1,3)]
  
  # Pivot from long form to a single row
  df <- df %>%
    pivot_wider(names_from = stat.name, values_from = base_stat)
  

  # If first iteration of loop, the final tibble  is created
  # If not the first iteration bind the final tibble from the previous loops 
  # with the new information
if( i == 1){
  final <- df
}else{
  final <- rbind(final,df)
} # End if else statement
  }# End loop
  
  # Return the final tibble.
  return(final)
} # End function
```

## Size Function

If you were interested in the heights and weights of Pokemon you can use the `size` function. The `size` function takes a single argument, `poke` that can be either a single character string of a Pokemon name, or a vector of names if you wanted the information on more than one Pokemon.

The output of the `size` function is a tibble with the Pokemons name, Height in meters, and Weight in kilograms.

```{r size_function}

# Create function.
size <- function(poke) {
  
  # Start loop if there is more than one Pokemon inputted.
  for(i in 1:length(poke)){
  
  # Get requested data from API.
  raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/pokemon/",poke[i]), flatten = TRUE)
  
  # Create objects to hold the height weight and name. 
  ht <- raw_data[["height"]]
  wt <- raw_data[["weight"]]
  Name <- str_to_sentence(poke[i])
  
  # Turn the objects into a tibble. 
  df <- tibble(Name,ht,wt)
  
  # If first iteration of loop, the final tibble  is created
  # If not the first iteration bind the final tibble from the previous loops 
  # with the new information
if( i == 1){
  final <- df
}else{
  final <- rbind(final,df)
} # End if else statement
  } # End loop
  
  # Edit the tibble before returning.
  # Height is stored decimeters, and weight as hectograms. 
  # We change them to meters and kilograms.
  # Finally select only the needed columns.
  final <- final %>%
    mutate(Height_Meters = ht / 10,
           Weight_Kilograms = wt / 10) %>%
    select(Name,Height_Meters,Weight_Kilograms)
    
   # Return the tibble.
  return(final)
} # End of function
```


## Dex Function

Throughout the Pokemon world there are various regions. Each region has their own Pokedex as each region has their own Pokemon, sometimes Pokemon can be found in multiple regions and other times they are only found in one region. There is also a "National Dex" that gives a unique number to every Pokemon in existence. The `dex` function is designed to look up the Pokedex entries for a given region or in all regions. 

The `dex` function takes two arguments, the first is `reg` which is the specific region the user is looking up. This will default to the National Dex if no region is chosen. The `reg` argument can accept either the character string version of the region name or the id number for the region (The relationship between the id number and name will be shown after the function is built). This can also be a single input or a vector.

The second argument is `poke` which is optional, this is to be used if you want to filter the results down to specific Pokemon. This can be a single character string or a vector of character strings. If no argument is provided, the function defaults to all Pokemon that are in the requested Pokedex(es). 

**OF NOTE THE API DOES NOT HAVE A REGION ID #10 IF YOU INCLUDE 10 IN THE `reg` ARGUMENT, THE FUNCTION WILL NOT WORK.**

```{r dex_function}

# Define function
dex <- function(reg = 1,poke = "all"){
  
  # Change both inputs to lower case for flexibility.
  reg <- tolower(reg)
  poke <- tolower(poke)
  
  
  # If "all" is selected for the reg argument, reg is defined as all available ID numbers.
  # If not reg remains what the user inputs.
  if( "all" %in% reg){
    reg <- c(1:9,11:29)
  }else{
    reg <- reg
  }  # End if else statement.
  
  # Begin Dex loop, for all Pokedexes requested.
  for(a in 1:length(reg)){
    
    # Get the data on the specific dex.
    raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/pokedex/",reg[a]), flatten = TRUE)
    
    # Save name of region
    dex_name <- str_to_sentence(raw_data[["name"]])
    
    # Begin poke loop for every Pokemon inside of specific dex.
    for(i in 1:dim(raw_data[["pokemon_entries"]])[1]){
      
      # Save the Pokedex entry number for the Pokemon.
      dex_num <- raw_data[["pokemon_entries"]][i,1]
      
      # Save the name of the Pokemon.
      nm <- str_to_sentence(raw_data[["pokemon_entries"]][i,2])
      
      # Combine the entry number and the name into a tibble.
      row_info <- tibble(nm,dex_num)
      
      # If first iteration of Poke loop, df is defined as the row_info tibble.
      # If not first iteration, df is combined with the latest row_info tibble to add new data.
      if(i == 1){
        df <- row_info
      }else{
        df <- rbind(df,row_info)
      } # End if else statement
    } # End Poke loop
    
    
    # Rename columns of df tibble, as Name for the Pokemons name and
    # (dex_name)_Dex_Number, so if the National Dex is the one being put together,
    # the column will be titled "National_Dex_Number".
    names(df) <- c("Name",paste0(dex_name,"_Dex_Number"))
    
    
    # If first iteration of Dex loop the final tibble is df tibble.
    # If not first iteration join final tibble and df tibble.
    if(a == 1){
      final <- df
    }else{
      final <- full_join(final,df,by = c("Name"="Name"))
    } # End of if else statement
  } # End of Dex loop
  
  
  # If user specifies Pokemon, filter the final tibble by defined inputs.
  if("all" %in% poke){
    final <- final
  }else{
    final <- final %>%
      filter(tolower(Name) %in% poke)
  } # End of if else statement.
  
  # Return final tibble.
  return(final)
  
} # End of function
```

Here is the relationship between the region names and their ID numbers.

```{r id table, echo = FALSE}
# Define function
get_all_ids <- function(x){
  
  # Begin loop
  for(i in 1:length(x)){
    
    # Get data from API
  raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/pokedex/",x[i]))
  
  # Save region ID number
  region_id <- raw_data[["id"]]
  
  # Save region name 
  region_name <- raw_data[["name"]]
  
  # Create tibble from name and id
  df <- tibble(region_id,region_name)
  
  # If first iteration of loop, final is the df tibble.
  # If not first iteration of loop, final is binded with df to add new data.
  if(i == 1){
    final <- df
  }else{
    final <- rbind(final,df)
  } # End if else statement
  
  } # End loop
  # Return final tibble
  return(final)
} # End of function

# Save the ids and names to the numbers object
numbers <- get_all_ids(c(1:9,11:29))

# Create table of ids and names.
kable(numbers)
```



## Egg Group Function

Another way to get new Pokemon is to breed the ones you already have. Pokemon can only breed with other Pokemon in their specific egg groups. For more information on egg groups click [here](https://bulbapedia.bulbagarden.net/wiki/Egg_Group). If you have a Pokemon and you want to know what egg group it is in for breeding purposes you can use the `egg_group` function! 

This function is designed to return a tibble with the Pokemons name and two columns of egg group data with it. The function takes two arguments and both are optional. The first is `group` which is for if the user wants to specify which egg group(s) data is returned on. If no argument is given then all groups will be returned. The inputs can be the character string for the name of the group or the id number for the group. This can be a single argument or a vector of them. The relationship between the names and ids will be shown after the function is built.

The second argument is `poke` which is if the user wants the data for only specific Pokemon. The function defaults to all Pokemon available in the selects group(s). The input can be either a single character string or a vector of them.


Every Pokemon belongs to at least one egg group even if that group is "no eggs". Some Pokemon will belong to two different egg groups, so the function is designed to always return two columns of egg groups, however if the specific Pokemon only belongs to one the second column will be `NA`. This is also true if the second egg group for the Pokemon is never searched.




```{r egg_group function}

# Build function
egg_group <- function(group = "all", poke = "all"){

  # Change inputs to lower to case to allow for some flexibility.
  group <- tolower(group)
  poke  <- tolower(poke)
  
  # If group is all, we change what group is defined as to the numbers for every egg group id.
  # If group is not all, group remains unchanged
  if(group == "all"){
    group <- c(1:15)
  }else{
    group <- group
  } # End if else statement
  
  # Begin loop for specific egg group.
for(i in 1:length(group)) {
  
  # Get the data we need from API.
raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/egg-group/",group[i]))

  # Save the name of the egg group as grp.
grp <- raw_data$name

   # Begin loop for Pokemon inside of egg group.
   for(a in 1:dim(raw_data$pokemon_species)[1]){
     
     # Save the name of the Pokemon as name.
     name <- raw_data$pokemon_species[a,1]
     
     # Create tibble with the name of the Pokemon and egg group.
     row_info <- tibble(name,grp)
     
     # If first iteration of Pokemon loop, the df tibble is defined as the row_info tibble.
     # If not first iteration, the df binded with row_info to add more inforamtion.
     if(a == 1){
       df <- row_info
     } else{
       df <- rbind(df,row_info)
     } # End of if else statement
   } # End of Pokemon for loop

    # Changing the names of the columns for easy joining.
    # The new column of egg groups is called _iteration with the iteration of the
    # egg group loop included before the _, this is to not overwrite previous data collected.
    names(df) <- c("name",paste0(i,"_iteration"))

     # If first iteration of egg group loop, the df2 tibble is defined as the most recent df tibble.
     # If not first iteration, the df2 tibble is full joined with df to add new data.
 if(i == 1){
  df2 <- df
 }else{
  df2 <- full_join(df2,df, by = c("name"= "name")) 
 } # End of if else statement.
} # End of egg group loop.
  
  # After the egg group loop is completed we are left with a tibble that is not
  # very descriptive and contains a lot of NAs. This section below helps to clean 
  # data for return.
  
  # Begin cleaning loop.
    for(b in 1:dim(df2)[1]){
      
      # Find columns for row b that are not NA and return a vector of 1s and 0s.
      row_na_info <- as.numeric(!is.na(df2[b,]))
      
      # This finds what position in the df2 tibble was not NA.
      not_na <- which(row_na_info %in% 1)
      
      # The first non NA is always the name, this is save as nm.
      nm <- df2[b,not_na[1]]
      
      # The second non NA is the first egg group for a Pokemon.
      # This is saved as group1.
      group1 <- df2[b,not_na[2]]
      
      # Not all Pokemon have two egg groups this if else statement accounts for that.
      # If there are three columns of non NA, group2 is defined as the second egg group.
      # If there are not three NA free columns, group2 is defined as NA.
      if(length(not_na) == 3){
        group2 <- df2[b,not_na[3]]
      }else{
        group2 <- NA
      } # End of if else statement.
      
      # Create new_row tibble, with cleaned name and egg group(s).
      new_row <- tibble(nm,group1,group2)
      
      # Rename columns
      names(new_row) <- c("Name","Egg_Group_1","Egg_Group_2")
      
      # If first iteration of cleaning loop, df3 is defined as the new_row tibble.
      # If not first iteration df3 is binded with new_row to add new data.
      if(b == 1){
      df3 <- new_row
      }else{
      df3 <- rbind(df3,new_row)
    } # End of if else statement.
} # End of cleaning loop

  # If user didn't specify Pokemon to return, the final tibble is defined as the most recent df3.
  # If user did specify df3 is filtered for the Pokemon and saved as the final tibble.
  if("all" %in% poke){
    final <- df3
  }else{
    final <- df3 %>%
      filter(Name %in% poke)
  } # End of if else statement.
  
  # Capitalize first letter of Pokemon name to match rest of functions.
  final$Name <- str_to_sentence(final$Name)
  
  # Return final tibble to user. 
  return(final)
} # End of function
```

Here is a table showing the relationship between the egg group id numbers and their associated names.

```{r egg group table, echo = FALSE}

# Define function
get_group_ids <- function(x){
  
  # Get requested data
  raw_data <- fromJSON("https://pokeapi.co/api/v2/egg-group/")
  
  # Begin loop
  for(i in 1:length(x)){
    
    # SAve group ID number.
    group_id <- x[i]
    
    # Save group name.
    group_name <- raw_data$results[["name"]][i]
    
    # create row for the group info
    group_row_info <- tibble(group_id,group_name)
    
    # If first iteration of loop final tibble is the group row info
    # If not bind final tibble with the newest group row info
    if(i == 1){
      final_tibble <- group_row_info
    }else{
      final_tibble <- rbind(final_tibble,group_row_info)
    } # End if else statement
} # End of loop

  # Return tibble
  return(final_tibble)
} # End Function

# Get the data for the table
egg_groups <- get_group_ids(c(1:15))

# create table
kable(egg_groups)
```


## Experience Function

When Pokemon battle they gain experience. This experience can make the Pokemon grow to a new level, when Pokemon reach a new level they upgrade their base stats that we looked at earlier and they can even evolve into new Pokemon.

Every Pokemon has a certain formula that defines how much experience it takes to get to the next level. These formulas can be read about [here](https://bulbapedia.bulbagarden.net/wiki/Experience). If you were interested in a question along the lines of "How much experience does it take for my Pokemon to reach level 50?" you can use the `exp_func`! 

`exp_func` is deigned to return a tibble with the Pokemons name, the name of the level formula used, and the experience needed to reach levels 1 through 100 (the maximum for every Pokemon). The function takes three arguments `rate`, `poke`, and `level`, all arguments are optional as they default to "all". They also all can take a single input or a vector of them.

`rate` is for the specific experience formulas you want to return data on, if you were wondering what Pokemon were in a certain formula group. You can define this as the name of the rate or the id number, the relationship between these will be shown after.

`poke` is for if you only want to return the data on specific Pokemon.

`level` is for what levels you would like to return data on, if not all. So if you wanted levels 10, 20, 30....level = c(10,20,30), would return the data for those levels.


```{r exp_func}
# Define function.
exp_func <- function(rate = "all",poke = "all",level = "all"){

  # Change inputs to lower case for variability in inputs.
rate <- tolower(rate)
poke <- tolower(poke)
level <- tolower(level) 

# Create empty object to be used later as the col names for the tibble.
level_vec <- as.character()

# If all rate are requested, rate is 1 through 6, if not rate is what was inputted.
if("all" %in% rate){
  rate <- c(1:6)
}else{
  rate <- rate
} # End if else statement

# Begin level for loop
# Create vector for future column names.
# Paste together "Level_" with the level number.
for(a in 1:100){
  level_vec[a] <- paste0("Level_",a)
} # End level for loop

# Begin rate loop.
# Returns all below data for requested rates.
for(i in 1:length(rate)){

  # Get the data about the specific rate from API.
raw_data <- fromJSON(paste0("https://pokeapi.co/api/v2/growth-rate/",rate[i]))

  # Save description of rate 
Description <- raw_data[["descriptions"]][["description"]][3]

  # Save experience required to reach ever level.
all_exp <- raw_data[["levels"]][["experience"]]

# Begin pokemon loop.
# Gets every Pokemon in the group.
for(b in 1:length(raw_data[["pokemon_species"]][["name"]])){
  
  # Save name of Pokemon.
  Name <- raw_data[["pokemon_species"]][["name"]][b]
  
  # Create tibble with name, description, required experience, and the future column names.
  row_info <- tibble(Name,Description,all_exp,level_vec)
 
  # if first iteration of pokemon loop, the df tibble is the row_info tibble.
  # if not first iteration of pokemon loop, the df tibble is binded with the the new row_info to add more data.
  if(b == 1){
    df <- row_info
  }else{
    df <- rbind(df,row_info)
  } # End if else statement.
} # End Pokemon loop

# The tibble at the end of the Pokemon loop is in long form.
# This changes it to wide form (one row per Pokemon) and saves as the df2 tibble.
df2 <- pivot_wider(df, id_cols = c(Name,Description), values_from = all_exp, names_from = level_vec)

# If first iteration of rate loop, the final tibble is the df2 tibble.
# If not first iteration, final tibble is binded with the newest df2 tibble.
if(i == 1){
  final <- df2
}else{
    final <- rbind(final,df2)
  } # End if else statement.
} # End of rate loop.


# If all Pokemon are requested to return, no change to the final tibble.
# If certain Pokemon are requested, the final tibble is filtered for them.
if("all" %in% poke){
  final <- final
}else{
  final <- final %>%
          filter(Name %in% poke)
} # End if else statement.

# If all levels are requested to return, no change to final tibble.
# If certain levels are requested we build the names of the columns to return,
# and select only those columns to return.
if("all" %in% level){
  final <- final
}else{
  lvl_vec <- as.character()
  
  for(c in 1:length(level)){
    lvl_vec[c] <- paste0("Level_",level[c])
  } 
  
  final <- final %>%
    select(Name,Description,lvl_vec)
}# End if else statement.

# Capitalize Names of Pokemon to match rest of functions.
final$Name <- str_to_sentence(final$Name)

# Return the final tibble.
return(final)

} # End of function
```

Here is the relationship between experience rate formula names and id numbers.

```{r rate table, echo = FALSE}

# get data from api.
raw_exp_data <- fromJSON("https://pokeapi.co/api/v2/growth-rate/")

# for loop to create tibble.
for(i in 1:6){
  # id num is also the iteration of the loop
  id_num <- i
  
  # Save the name of the rate.
  exp_name <- raw_exp_data[["results"]][["name"]][i]
  
  # Build tibble.
  exp_df1 <- tibble(id_num,exp_name)
  
  # If first iteration of loop, the exp_df2 tibble is exp_df1.
  # If not, exp_df2 is binded with exp_df1 to add new data.
  if(i == 1){
    exp_df2 <- exp_df1
  } else{
    exp_df2 <- rbind(exp_df2,exp_df1)
  } # End if else statement.
} # End for loop

# Print tibble.
kable(exp_df2)
```





# Basic Functionality

Below we show a basic example of each function.

## Encounter Example

Here we test the encounter function with my favorite starter Pokemon **CHARMANDER**.

```{r encounter example}
# Use the function and save results in an object
charmander <- encounter("charmander")

# Print the object
print(charmander)
```

## Stats Example

Here is an example of the `stats` function, with a vector of four Pokemon.

```{r stats example}
# Create a vector of four Pokemon
mons <- c("charizard","pidgey","abra","beedrill") 

# Use the function on the vector
stat_example <- stats(mons)

# Print results
print(stat_example)
```


## Size Example

Here we test the `size` function, with the same vector of four Pokemon from the `stats` example.


```{r size example}
# Use the function on the vector
size_example <- size(mons)

# Print results
print(size_example)
```

## Dex Example

Here we test the `dex` function. We are using regions with dex ids 1 through 5, and only returning results on our same four Pokemon from the previous two examples. Any `NA` means that the Pokemon is not in that Pokedex.

```{r dex example}
# Use function on vectors
dex_example <- dex(reg = c(1:5), poke = mons)

# Print results
print(dex_example)
```

## Egg Group Example

Here we test the `egg_group` function. We are using all egg groups, and returning the information for the Pokemon in our `mons` vector that we have been using. Any `NA` means the Pokemon doesn't have a second egg group.

```{r egg_group example}

# Use function on mons vector.
egg_example <- egg_group(group = "all", poke = mons)

# Return the tibble.
print(egg_example)
```

## Experience Function Example

Here we test the `exp_func` function. We are using all rate groups, the same `mons` vector we have been using, and levels 10, 25, 50, 75, and 100.

```{r exp example}

# Use function on mons vector and for the specific levels we want.
exp_example <- exp_func(rate = "all", poke = mons, level = c(10,25,50,75,100))

# Return the tibble.
print(exp_example)
```



